### 2015-11-09 postdoctoral/S_prime_kappa.tex
start writing up notes based on alan's input

  \begin{proof}
    Assume we've defined such a topology for \(\omega_k\)
    such that \(\gamma+1=[0,\gamma]\) is clopen for all \(\gamma<\omega_k\).
    Note that the usual linear order on \(\omega_1\) satisfies these requirements.

    Let \(\alpha<\omega_{k+1}\), and suppose we've defined compatible topologies on
    \(\omega_k\cdot (\beta+1)\) for all \(0\leq\beta<\alpha\).
    If \(\alpha=\beta+1\), then let
    \(\omega_k\cdot(\alpha+1)=\omega_k\cdot(\beta+2)\) be the topological sum
    of the previously defined \(\omega_k\cdot(\beta+1)\) and the
    previously defined
    \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\).
    Similarly, if \(cf(\alpha)>\omega\), then let \(\omega_k\cdot(\alpha+1)\)
    be the topological sum of \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\)
    and the previously defined
    \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\).

    The remaining case is where \(\alpha\) is the limit of increasing
    \(\alpha_n\) for \(n<\omega\). Fix a bijection
    \(
      f_\alpha
        :
      \omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha
        \to
      \omega_k\cdot\alpha
    \). Points in \(\omega_k\cdot(\alpha_n+1)\) for some \(n<\omega\)
    have their usual base induced by that previously defined topology. So let
    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\).
    Basic open neighborhoods of \(\gamma\) are of the form
    \(
      W
        \cup
      f_\alpha[W]
        \setminus
      \omega_k\cdot(\alpha_n+1)
    \),
    where \(n<\omega\) and
    \(W\subseteq\gamma+1\) is any countable neighborhood of \(\gamma\).

    We wish to show that \(\omega_{k+1}\) with the topology induced by
    \(\bigcup_{\alpha<\omega_{k+1}}\omega_k\cdot(\alpha+1)\) is \(\omega\)-bounded
    and locally countable. If
    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\) where
    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
    copy of \(\omega_k\) giving us local countability
    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
    \(
      W
        \cup
      f_\alpha[W]
        \setminus
      \omega_k\cdot(\alpha_n+1)
    \),
    which is obviously countable.

    Let \(C\) be a countable subset of \(\omega_k\cdot(\alpha+1)\).
    In the case that \(\alpha=\beta+1\), we may use the \(\omega\)-boundedness
    of each part in the clopen partition \(\omega_k\cdot(\beta+1)\) and
    \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\)
    to conclude that the closure of \(C\) is compact.
    Similarly, if \(cf(\alpha)>\omega\),
    then we may use the  \(\omega\)-boundedness
    of each part in the clopen partition
    \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\) and
    \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\)
    to conclude that the closure of \(C\) is compact.

    The remaining case is again where \(\alpha\) is the limit of increasing
    \(\alpha_n\) for \(n<\omega\). Then
    TODO: generalize for \(k+1\)
    % \(
    %   C
    %     \subseteq
    %   [\gamma',\gamma]
    %     \cup
    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
    % \)
    % for some \(\omega_k\cdot\alpha\leq\gamma'<\gamma<\omega_k\cdot(\alpha+1)\).
    % Its closure is compact:
    % the closure operation does not add any ordinals greater than \(\gamma\),
    % and any open cover
    % contains another basic open neighborhood of \(\gamma\) such as
    % \(
    %   [\gamma'',\gamma]
    %     \cup
    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
    %     \setminus
    %   \omega_k\cdot(\alpha_m+1)
    % \)
    % which misses only the compact set \([\gamma',\gamma'']\) and the
    % closure of the countable set
    % \(
    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
    %     \cap
    %   \omega_k\cdot(\alpha_{\min(m,n)}+1)
    % \), which is compact by the \(\omega\)-boundedness of
    % \(\omega_k\cdot(\alpha_{\min(m,n)}+1)\).

    Finally, since every countable subset of \(\omega_{k+1}\) is contained in
    some \(\omega_k\cdot(\alpha+1)\), we conclude \(\omega_{k+1}\) is
    \(\omega\)-bounded.
  \end{proof}

  \begin{theorem*}
    \(S'(\omega_\omega)\).
  \end{theorem*}

>>>>

  \begin{proof}
    TODO: write up Alan's proof
  \end{proof}

  \begin{definition}
    A Kurepa family \(\mc K\)
    is a family of countable sets such that for each \(A\in\mc K\),
    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable.
  \end{definition}

  \begin{corollary}
    There exists a Kurepa family cofinal in \([\omega_k]^\omega\)
    for each \(k<\omega\).
  \end{corollary}

  \begin{proof}
    This is actually a corollary of an observation of Todorcevic communicated
    by Dow in [TODO cite Gen Prog in Top I]:
    if every Kurepa family of size at most \(\theta\)
    extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
    So the result follows as
    every Kurepa family of size \(\omega\) extends to
    the cofinal Kurepa family \([\omega]^\omega\). (TODO am I understanding
    this right?)

    We may alternatively
    obtain the result from the previous topological argument by using the family
    \(\mc K\) of compact sets in the constructed topology on
    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable. Thus \(\mc K\)
    is cofinal since for every countable set \(A\), \(\cl A\) is compact
    and countable.
    It is Kurepa since for every compact (countable) set \(A\), (TODO).
  \end{proof}

  \begin{theorem}
    \(S'(\omega_k)\) for each \(k<\omega\).
  \end{theorem}

  \begin{proof}
    Let \(k<\omega\), and \(\mc K\) be a cofinal Kurepa family on \(\omega_k\).
    (TODO finish)
  \end{proof}
